%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a LaTeX template for students
% working on Homework 6, Computer Architecture I, Spring, 2022.
% You SHALL NOT distribute this template.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{One more thing...}
Phew! That's all about cache! Tell us your feeling after finish this
homework. Thank You! Don't worry if you did not assign this to
Gradescope. This part is \emph{optional}.

\begin{questions}

\question[0] How do you \emph{feel} after you have done this homework?

{
    \begin{solution}
        \begin{checkboxes}
            \CorrectChoice :) I feel good.
            \choice :( I feel bad.
        \end{checkboxes}
    \end{solution}
}

\question[0] Do you think this homework is hard for you?

{
    \begin{solution}
        \begin{checkboxes}
            \choice It's really difficult for me!
            \choice I think it is a little bit challenging.
            \CorrectChoice I am okay with that.
            \choice This is too easy for me.
        \end{checkboxes}
    \end{solution}
}

\question[0] Your voice will be secretly heard by our team.
Is there anything you want to feedback?

{
    \begin{solution}
        \begin{enumerate}
            \item This homework is not problematic at all, good job!
            \item However, as for course projects, I think they should be more practical, complicated, integrated and well correlated to the real-world programs, rather than simply implementing a boring RV32I-RVC bidirectional translator or building a CPU. In fact if you really want us to do so, set them to be homework may be better.
        \end{enumerate}
    \end{solution}
}

\vspace*{\fill}
\begin{center}
\Large Thank you! Now you are clear with cache! :)
\end{center}

\end{questions}